Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2016-09-24 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added FDS comparison figures
also copied original .cls file into repo

@@

@@

@@

>>>>

\begin{figure}[ht!]
  \centering
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_2D_RI}
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_1D_RI}\\
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_0pD_RI}
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_0D_RI}\\
  \caption[FDS values based on three different resolutions compared with plume temperature measurements along the centerline of the natural gas fueled burner]{FDS values based on three different resolutions compared with plume temperature measurements along the centerline of the natural gas fueled burner. The temperatures are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
  \label{FDS_Plume_Grid_TWNG_comp}
\end{figure}

@@

\subsection{Temperatures}

\begin{figure}[ht!]
  \centering
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_2D}
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_1D}\\
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_0p5D}
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_0D}\\
  \caption[FDS values based on 40~mm grid compared with plume temperature measurements along the centerline of the natural gas fueled burner]{FDS values based on 40~mm grid compared with plume temperature measurements along the centerline of the natural gas fueled burner. The temperatures are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
  \label{FDS_TCPlume_TWNG_comp}
\end{figure}

\begin{figure}[ht!]
  \centering
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_2D}
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_1D}\\
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_0p5D}
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_0D}\\
  \caption[FDS values based on 40~mm grid compared with the wall temperature measurements along the centerline of the natural gas fueled burner]{FDS values based on 40~mm grid compared with the wall temperature measurements along the centerline of the natural gas fueled burner. The temperatures are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
  \label{FDS_TCWall_TWNG_comp}
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_2D}
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_1D}\\
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_0p5D}
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_0D}\\
  \caption[FDS values based on 40~mm grid compared with heat flux measurements on the wall along the centerline of the natural gas fueled burner]{FDS values based on 40~mm grid compared with heat flux measurements on the wall along the centerline of the natural gas fueled burner. The temperatures are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
  \label{FDS_HFCL_TWNG_comp}
\end{figure}

\begin{figure}[ht!]
  \centering
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Offset_Avg_2D}
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Offset_Avg_1D}\\
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Offset_Avg_0p5D}
  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Offset_Avg_0D}\\
  \caption[FDS values based on 40~mm grid compared with heat flux measurements on the wall along the right edge of the natural gas fueled burner]{FDS values based on 40~mm grid compared with heat flux measurements on the wall along the right edge of the natural gas fueled burner. The temperatures are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
  \label{FDS_HFEdge_TWNG_comp}
\end{figure}

@@

Table to compare measured flame height with FDS cal.
